Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-06-25 Paper/paper.tex
abstract

We examine the effects of level of immersion and tracking sensor reliability in augmented reality (AR) X-ray vision with a virtual reality (VR) based simulation.  We analyze participant performance on a target following task while varying the field of view of the AR display, as well as the reliability of the head tracking sensor.  In low reliability conditions, we simulate sensor dropouts by disabling the augmented view of the scene for brief time periods.  Our study gives insight into the effect of tracking sensor reliability on user performance in a target following task, as well as the relationship between sensor reliability and field of view in an AR system.

>>>>

We examine the effect of varying levels of immersion on the performance of a target following task in simulated augmented reality (AR) X-ray vision.  We do this using virtual reality (VR) based simulation.  We analyze participant performance while varying the field of view of the simulated AR display, as well as the reliability of the head tracking sensor as our factors of immersion.  In low reliability conditions, we simulate sensor dropouts by disabling the augmented view of the scene for brief time periods.  Our study gives insight into the effect of tracking sensor reliability , as well as the relationship between sensor reliability and field of view on user performance in a target following task in a simulated AR system.
